Individual heterogeneity in the functional network topography of medial prefrontal cortex

### 2019-08-19 Manuscript.Rmd
rearranging figure location
added ARI simulation example and fixed a tiny bug in thresholding communities in example script

## Figures

@@

```{r ARI Comparison (supplemental fig 2), out.width = "50%", fig.align = "center", fig.cap = "Example of an across-day comparison using ARI for two subjects (100307 and 100408). This reflects how qualitatively similar, within-subject partitionings can have relatively small ARI values (here 0.24-0.25), and how partitionings across individuals are much closer to the chance level of zero."}
include_graphics("./Images/ARI_comparison.png")
```

>>>>

@@

```{r ARI Comparison (supplemental fig 2), out.width = "50%", fig.align = "center", fig.cap = "Example of an across-day comparison using ARI for two subjects (100307 and 100408). This reflects how qualitatively similar, within-subject partitionings can have relatively small ARI values (here 0.24-0.25), and how partitionings across individuals are much closer to the chance level of zero."}
include_graphics("./Images/ARI_comparison.png")

# # the second plot (simulation), showing decay of similarity as differences increase
# library(mcclust)
# library(reshape2)
# 
# # Produce a random vector with 100 binary classifications
# n <- 4801
# v1 <- rbinom(n = n, size = 1, prob = 0.5)
# 
# # Data frame to store evaluations
# evals <- data.frame(Diffs = seq(n),
#                     ARI = rep(0,n),
#                     RI = rep(0,n),
#                     EQ = rep(0,n))
# 
# # Check the degree of agreement per metric for each incremental switch in affiliation
# for (i in seq(n)) {
#   
#   # Switch affiliation up to the ith node
#   ifelse(i < n, v2temp <- c((1 - v1[seq(i)]), v1[(i+1):n]), v2temp <- v1)
#   
#   # Evaluate
#   evals$ARI[i] <- arandi(v1,v2temp)
#   evals$RI[i] <- arandi(v1,v2temp, adjust = F)
#   evals$EQ[i] <- mean(v1 == v2temp)
#   
# }
# 
# # Make the data.frame long instead of wide for ggplot
# evals <- melt(evals[seq(n-1),], id.vars = "Diffs")
# 
# # And plot
# ggplot(data = evals, aes(Diffs, value, group = variable, color = variable)) + 
#   geom_line(size = 1.5) +
#   labs(x = "Number of Class Differences", y = "Similarity Value") +
#   scale_color_discrete(name = "Method") +
#   scale_x_continuous(breaks = c(seq(0, 4000, by = 1000), 4801)) +
#   theme(legend.position = c(0.9, 0.32),
#         legend.key=element_blank(),
#         panel.grid.major = element_blank(), 
#         panel.grid.minor = element_blank(), 
#         panel.background = element_blank(), 
#         axis.line = element_line(colour = "black"),
#         text = element_text(size = 22))
```
